The Free-play Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
Add back the description of the sandtray

The background image depicts a contextual environment, with different 
zones (for example, water, grass, path, bushes...). Additionally, the children can draw on
the background using a tool of the colour is costumisable. The players do
not have any particular task to complete, they are simply invited to freely
play. Importantly, they can play for as long as they wish (for
practical reasons, we have limited the sessions to a maximum of 40 minutes in
our own experiments, see Section~\ref{sec:dataset}).

>>>>

The free-play sandbox follows the sandtray
paradigm~\cite{baxter2012touchscreen}: a large touchscreen (60cm $\times$ 33cm,
with multitouch support) is used as an interactive surface (\emph{sandtray}).
Two children play together by freely moving interactive items on the surface
(Fig.~\ref{fig|sandbox}). A background image depicts a generic empty
environment, with different symbolic colours (water, grass, beach, bushes...).
By drawing on top of the background picture, the children can change the
environment to their liking. The players do not have any particular task to
complete, they are simply invited to freely play. Importantly, they can play for
as long as they wish (for practical reasons, we have limited the sessions to a
maximum of 40 minutes in our own experiments, see Section~\ref{sec:dataset}).
